---
title: "Fitting time series data to pool models"
author: "Mina Azizi-Rad"
date: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
packs <- c('SoilR', 'sidb', 'R.utils', 'dplyr')
sapply(packs, require, character.only=TRUE)
rm(list=ls())

```

```{r upload the database, results='hide', include=FALSE}

####### Function uploading #######
source(file = "/Users/mina/sidb/manuscript/ModFitTS_Rmd_Func.R")

###### Upload the database ######
db=loadEntries(path="~/sidb/data/")
#db_flat=flatterSIDb(db)
###############
```

# Dataset `r db[[4]]$citationKey`

## Variable `r db[[4]]$variables$V2$name`;
`r db[[4]]$variables$V2$varDesc`
```{r }
Brach0_V2=modelFitTS_Markdown(db = db[[4]], ts.col = 2, ic.col = 1, unitConverter = 1e3, 
                               inipars=list(oneP=0.5,
                                            parallel=c(0.01, 0.001, 0.1),
                                            series=c(0.01, 0.001, 0.01, 0.1),
                                            feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[4]]$variables$V4$name`;
`r db[[4]]$variables$V4$varDesc`
```{r}

Brach0_V4=modelFitTS_Markdown(db = db[[4]], ts.col = 4, ic.col = 2, unitConverter = 100, 
                     inipars=list(oneP=0.5,
                                  parallel=c(0.01, 0.001, 0.1),
                                  series=c(0.01, 0.001, 0.01, 0.1),
                                  feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[4]]$variables$V6$name`;
`r db[[4]]$variables$V6$varDesc`
```{r}
Brach0_V6=modelFitTS_Markdown(db = db[[4]], ts.col = 6, ic.col = 3, unitConverter = 100, 
                     inipars=list(oneP=0.5,
                                  parallel=c(0.01, 0.001, 0.1),
                                  series=c(0.01, 0.001, 0.01, 0.1),
                                  feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[4]]$variables$V8$name`;
`r db[[4]]$variables$V8$varDesc`
```{r}
Brach0_V8=modelFitTS_Markdown(db = db[[4]], ts.col = 8, ic.col = 4, unitConverter = 1000, 
                     inipars=list(oneP=0.5,
                                  parallel=c(0.01, 0.001, 0.1),
                                  series=c(0.01, 0.001, 0.01, 0.1),
                                  feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[4]]$variables$V10$name`;
`r db[[4]]$variables$V10$varDesc`
```{r}
Brach0_V10=modelFitTS_Markdown(db = db[[4]], ts.col = 10, ic.col = 5, unitConverter = 1000, 
                      inipars=list(oneP=0.5,
                                   parallel=c(0.01, 0.001, 0.1),
                                   series=c(0.01, 0.001, 0.01, 0.1),
                                   feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[4]]$variables$V12$name`;
`r db[[4]]$variables$V12$varDesc`
```{r}
Brach0_V12=modelFitTS_Markdown(db = db[[4]], ts.col = 12, ic.col = 6, unitConverter = 100, 
                     inipars=list(oneP=0.5,
                                  parallel=c(0.01, 0.001, 0.1),
                                  series=c(0.01, 0.001, 0.01, 0.1),
                                  feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

# Dataset `r db[[9]]$citationKey`

## Variable `r db[[9]]$variables$V2$name`;
`r db[[9]]$variables$V2$varDesc`
```{r}
Crow_V2=modelFitTS_Markdown(db = db[[9]], ts.col = 2, ic.col = 1, unitConverter = 1e3)
```

## Variable `r db[[9]]$variables$V3$name`;
`r db[[9]]$variables$V3$varDesc`
```{r}

Crow_V3=modelFitTS_Markdown(db = db[[9]], ts.col = 3, ic.col = 2, unitConverter = 1e3) #,
```

## Variable `r db[[9]]$variables$V4$name`;
`r db[[9]]$variables$V4$varDesc`
```{r}
Crow_V4=modelFitTS_Markdown(db = db[[9]], ts.col = 4, ic.col = 3, unitConverter = 1e3,
              inipars=list(oneP=0.5,
                           parallel=c(0.01, 0.001, 0.1),
                           series=c(0.05, 0.0001, 0.01, 0.1),
                           feedback=c(0.05, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V5$name`;
`r db[[9]]$variables$V5$varDesc`
```{r}

Crow_V5=modelFitTS_Markdown(db = db[[9]], ts.col = 5, ic.col = 4, unitConverter = 1e3)
```

## Variable `r db[[9]]$variables$V6$name`;
`r db[[9]]$variables$V6$varDesc`
```{r}

Crow_V6=modelFitTS_Markdown(db = db[[9]], ts.col = 6, ic.col = 5, unitConverter = 1e3,
              inipars=list(oneP=0.5,
                           parallel=c(0.01, 0.001, 0.1),
                           series=c(0.05, 0.0001, 0.01, 0.1),
                           feedback=c(0.05, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V7$name`;
`r db[[9]]$variables$V7$varDesc`
```{r}

Crow_V7=modelFitTS_Markdown(db = db[[9]], ts.col = 7, ic.col = 6, unitConverter = 1e3,
              inipars=list(oneP=0.5,
                           parallel=c(0.01, 0.001, 0.1),
                           series=c(0.05, 0.0001, 0.01, 0.1),
                           feedback=c(0.05, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V8$name`;
`r db[[9]]$variables$V8$varDesc`
```{r}

Crow_V8=modelFitTS_Markdown(db = db[[9]], ts.col = 8, ic.col = 7, unitConverter = 1e3,
              inipars=list(oneP=0.5,
                           parallel=c(0.01, 0.001, 0.1),
                           series=c(0.01, 0.0001, 0.01, 0.1),
                           feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V9$name`;
`r db[[9]]$variables$V9$varDesc`
```{r}

Crow_V9=modelFitTS_Markdown(db = db[[9]], ts.col = 9, ic.col = 8, unitConverter = 1e3,
              inipars=list(oneP=0.5,
                           parallel=c(0.01, 0.001, 0.1),
                           series=c(0.01, 0.0001, 0.01, 0.1),
                           feedback=c(0.05, 0.0001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[9]]$variables$V10$name`;
`r db[[9]]$variables$V10$varDesc`
```{r}

Crow_V10=modelFitTS_Markdown(db = db[[9]], ts.col = 10, ic.col = 9, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.001, 0.1, 0.01, 0.01)))
```


## Variable `r db[[9]]$variables$V11$name`;
`r db[[9]]$variables$V11$varDesc`
```{r}
# The models get fitted but the folowing error prevents the data to be saved
# Error in solve.default(A) :
#   system is computationally singular: reciprocal condition number = 1.37957e-17

Crow_V11=modelFitTS_Markdown(db = db[[9]], ts.col = 11, ic.col = 10, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.01, 0.0001, 0.01, 0.1),
                            feedback=c(0.05, 0.0001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[9]]$variables$V12$name`;
`r db[[9]]$variables$V12$varDesc`
```{r}

Crow_V12=modelFitTS_Markdown(db = db[[9]], ts.col = 12, ic.col = 11, unitConverter = 1e3)
```

## Variable `r db[[9]]$variables$V13$name`;
`r db[[9]]$variables$V13$varDesc`
```{r}

Crow_V13=modelFitTS_Markdown(db = db[[9]], ts.col = 13, ic.col = 12, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0005, 0.01, 0.1),
                            feedback=c(0.05, 0.0001, 0.1, 0.01, 0.01)) )
```

## Variable `r db[[9]]$variables$V14$name`;
`r db[[9]]$variables$V14$varDesc`
```{r}

Crow_V14=modelFitTS_Markdown(db = db[[9]], ts.col = 14, ic.col = 13, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V15$name`;
`r db[[9]]$variables$V15$varDesc`
```{r}

Crow_V15=modelFitTS_Markdown(db = db[[9]], ts.col = 15, ic.col = 14, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V16$name`;
`r db[[9]]$variables$V16$varDesc`
```{r}

Crow_V16=modelFitTS_Markdown(db = db[[9]], ts.col = 16, ic.col = 15, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V17$name`;
`r db[[9]]$variables$V17$varDesc`
```{r}

Crow_V17=modelFitTS_Markdown(db = db[[9]], ts.col = 17, ic.col = 16, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.01, 0.0001, 0.05, 0.1),
                            feedback=c(0.05, 0.0005, 0.1, 0.01, 0.01)))
```

## Variable `r db[[9]]$variables$V18$name`;
`r db[[9]]$variables$V18$varDesc`
```{r}

Crow_V18=modelFitTS_Markdown(db = db[[9]], ts.col = 18, ic.col = 17, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V19$name`;
`r db[[9]]$variables$V19$varDesc`
```{r}

Crow_V19=modelFitTS_Markdown(db = db[[9]], ts.col = 19, ic.col = 18, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.01, 0.0001, 0.05, 0.1),
                            feedback=c(0.05, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V20$name`;
`r db[[9]]$variables$V20$varDesc`
```{r}

Crow_V20=modelFitTS_Markdown(db = db[[9]], ts.col = 20, ic.col = 19, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V21$name`;
`r db[[9]]$variables$V21$varDesc`
```{r}

Crow_V21=modelFitTS_Markdown(db = db[[9]], ts.col = 21, ic.col = 20, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.01, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0001, 0.1, 0.01, 0.01)) )
```

## Variable `r db[[9]]$variables$V22$name`;
`r db[[9]]$variables$V22$varDesc`
```{r}

Crow_V22=modelFitTS_Markdown(db = db[[9]], ts.col = 22, ic.col = 11, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0001, 0.1, 0.01, 0.01)) )
```

## Variable `r db[[9]]$variables$V23$name`;
`r db[[9]]$variables$V23$varDesc`
```{r}

Crow_V23=modelFitTS_Markdown(db = db[[9]], ts.col = 23, ic.col = 22, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V24$name`;
`r db[[9]]$variables$V24$varDesc`
```{r}

Crow_V24=modelFitTS_Markdown(db = db[[9]], ts.col = 24, ic.col = 23, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V25$name`;
`r db[[9]]$variables$V25$varDesc`
```{r}

Crow_V25=modelFitTS_Markdown(db = db[[9]], ts.col = 25, ic.col = 24, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V26$name`;
`r db[[9]]$variables$V26$varDesc`
```{r}

Crow_V26=modelFitTS_Markdown(db = db[[9]], ts.col = 26, ic.col = 25, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V27$name`;
`r db[[9]]$variables$V27$varDesc`
```{r}

Crow_V27=modelFitTS_Markdown(db = db[[9]], ts.col = 27, ic.col = 26, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V28$name`;
`r db[[9]]$variables$V28$varDesc`
```{r}

Crow_V28=modelFitTS_Markdown(db = db[[9]], ts.col = 28, ic.col = 27, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V29$name`;
`r db[[9]]$variables$V29$varDesc`
```{r}

Crow_V29=modelFitTS_Markdown(db = db[[9]], ts.col = 29, ic.col = 28, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1)) )
```

## Variable `r db[[9]]$variables$V30$name`;
`r db[[9]]$variables$V30$varDesc`
```{r}

Crow_V30=modelFitTS_Markdown(db = db[[9]], ts.col = 30, ic.col = 29, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V31$name`;
`r db[[9]]$variables$V31$varDesc`
```{r}
Crow_V31=modelFitTS_Markdown(db = db[[9]], ts.col = 31, ic.col = 30, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V32$name`;
`r db[[9]]$variables$V32$varDesc`
```{r}
Crow_V32=modelFitTS_Markdown(db = db[[9]], ts.col = 32, ic.col = 31, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V33$name`;
`r db[[9]]$variables$V33$varDesc`
```{r}
Crow_V33=modelFitTS_Markdown(db = db[[9]], ts.col = 33, ic.col = 32, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V34$name`;
`r db[[9]]$variables$V34$varDesc`
```{r}
Crow_V34=modelFitTS_Markdown(db = db[[9]], ts.col = 34, ic.col = 33, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V35$name`;
`r db[[9]]$variables$V35$varDesc`
```{r}
Crow_V35=modelFitTS_Markdown(db = db[[9]], ts.col = 35, ic.col = 34, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V36$name`;
`r db[[9]]$variables$V36$varDesc`
```{r}
Crow_V36=modelFitTS_Markdown(db = db[[9]], ts.col = 36, ic.col = 35, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.01, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V37$name`;
`r db[[9]]$variables$V37$varDesc`
```{r}
##
Crow_V37=modelFitTS_Markdown(db = db[[9]], ts.col = 37, ic.col = 36, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1)) )
```

## Variable `r db[[9]]$variables$V38$name`;
`r db[[9]]$variables$V38$varDesc`
```{r}

Crow_V38=modelFitTS_Markdown(db = db[[9]], ts.col = 38, ic.col = 37, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V39$name`;
`r db[[9]]$variables$V39$varDesc`
```{r}
Crow_V39=modelFitTS_Markdown(db = db[[9]], ts.col = 39, ic.col = 38, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V40$name`;
`r db[[9]]$variables$V40$varDesc`
```{r}
Crow_V40=modelFitTS_Markdown(db = db[[9]], ts.col = 40, ic.col = 39, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V41$name`;
`r db[[9]]$variables$V41$varDesc`
```{r}
Crow_V41=modelFitTS_Markdown(db = db[[9]], ts.col = 41, ic.col = 40, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V42$name`;
`r db[[9]]$variables$V42$varDesc`
```{r}
Crow_V42=modelFitTS_Markdown(db = db[[9]], ts.col = 42, ic.col = 41, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V43$name`;
`r db[[9]]$variables$V43$varDesc`
```{r}
Crow_V43=modelFitTS_Markdown(db = db[[9]], ts.col = 43, ic.col = 42, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V44$name`;
`r db[[9]]$variables$V44$varDesc`
```{r}
Crow_V44=modelFitTS_Markdown(db = db[[9]], ts.col = 44, ic.col = 43, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V45$name`;
`r db[[9]]$variables$V45$varDesc`
```{r}
Crow_V45=modelFitTS_Markdown(db = db[[9]], ts.col = 45, ic.col = 44, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V46$name`;
`r db[[9]]$variables$V46$varDesc`
```{r}
Crow_V46=modelFitTS_Markdown(db = db[[9]], ts.col = 46, ic.col = 45, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V47$name`;
`r db[[9]]$variables$V47$varDesc`
```{r}
Crow_V47=modelFitTS_Markdown(db = db[[9]], ts.col = 47, ic.col = 46, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V48$name`;
`r db[[9]]$variables$V48$varDesc`
```{r}
Crow_V48=modelFitTS_Markdown(db = db[[9]], ts.col = 48, ic.col = 47, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V49$name`;
`r db[[9]]$variables$V49$varDesc`
```{r}
Crow_V49=modelFitTS_Markdown(db = db[[9]], ts.col = 49, ic.col = 48, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V50$name`;
`r db[[9]]$variables$V50$varDesc`
```{r}
Crow_V50=modelFitTS_Markdown(db = db[[9]], ts.col = 50, ic.col = 49, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V51$name`;
`r db[[9]]$variables$V51$varDesc`
```{r}
Crow_V51=modelFitTS_Markdown(db = db[[9]], ts.col = 51, ic.col = 50, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V52$name`;
`r db[[9]]$variables$V52$varDesc`
```{r}
Crow_V52=modelFitTS_Markdown(db = db[[9]], ts.col = 52, ic.col = 51, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.01, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V53$name`;
`r db[[9]]$variables$V53$varDesc`
```{r}
Crow_V53=modelFitTS_Markdown(db = db[[9]], ts.col = 53, ic.col = 52, unitConverter = 1e3 ,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V54$name`;
`r db[[9]]$variables$V54$varDesc`
```{r}
Crow_V54=modelFitTS_Markdown(db = db[[9]], ts.col = 54, ic.col = 53, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V55$name`;
`r db[[9]]$variables$V55$varDesc`
```{r}
Crow_V55=modelFitTS_Markdown(db = db[[9]], ts.col = 55, ic.col = 54, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V56$name`;
`r db[[9]]$variables$V56$varDesc`
```{r}
Crow_V56=modelFitTS_Markdown(db = db[[9]], ts.col = 56, ic.col = 55, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)) )
```

## Variable `r db[[9]]$variables$V57$name`;
`r db[[9]]$variables$V57$varDesc`
```{r}

Crow_V57=modelFitTS_Markdown(db = db[[9]], ts.col = 57, ic.col = 56, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V58$name`;
`r db[[9]]$variables$V58$varDesc`
```{r}
Crow_V58=modelFitTS_Markdown(db = db[[9]], ts.col = 58, ic.col = 57, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)) )
```

## Variable `r db[[9]]$variables$V59$name`;
`r db[[9]]$variables$V59$varDesc`
```{r}
Crow_V59=modelFitTS_Markdown(db = db[[9]], ts.col = 59, ic.col = 58, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V60$name`;
`r db[[9]]$variables$V60$varDesc`
```{r}
Crow_V60=modelFitTS_Markdown(db = db[[9]], ts.col = 60, ic.col = 59, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V61$name`;
`r db[[9]]$variables$V61$varDesc`
```{r}
Crow_V61=modelFitTS_Markdown(db = db[[9]], ts.col = 61, ic.col = 59, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V62$name`;
`r db[[9]]$variables$V62$varDesc`
```{r}
Crow_V62=modelFitTS_Markdown(db = db[[9]], ts.col = 62, ic.col = 61, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)) )
```

## Variable `r db[[9]]$variables$V63$name`;
`r db[[9]]$variables$V63$varDesc`
```{r}
Crow_V63=modelFitTS_Markdown(db = db[[9]], ts.col = 63, ic.col = 62, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V64$name`;
`r db[[9]]$variables$V64$varDesc`
```{r}
Crow_V64=modelFitTS_Markdown(db = db[[9]], ts.col = 64, ic.col = 63, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V65$name`;
`r db[[9]]$variables$V65$varDesc`
```{r}
Crow_V65=modelFitTS_Markdown(db = db[[9]], ts.col = 65, ic.col = 64, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1))  )
```

## Variable `r db[[9]]$variables$V66$name`;
`r db[[9]]$variables$V66$varDesc`
```{r}
Crow_V66=modelFitTS_Markdown(db = db[[9]], ts.col = 66, ic.col = 65, unitConverter = 1e3 ,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.05, 0.0005, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V67$name`;
`r db[[9]]$variables$V67$varDesc`
```{r}
Crow_V67=modelFitTS_Markdown(db = db[[9]], ts.col = 67, ic.col = 66, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.05, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)) )
```

## Variable `r db[[9]]$variables$V68$name`;
`r db[[9]]$variables$V68$varDesc`
```{r}

##
Crow_V68=modelFitTS_Markdown(db = db[[9]], ts.col = 68, ic.col = 67, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.01, 0.001, 0.1),
                            series=c(0.01, 0.0005, 0.01, 0.1),
                            feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1))  )
```

## Variable `r db[[9]]$variables$V69$name`;
`r db[[9]]$variables$V69$varDesc`
```{r}
Crow_V69=modelFitTS_Markdown(db = db[[9]], ts.col = 69, ic.col = 68, unitConverter = 1e3 )
```

## Variable `r db[[9]]$variables$V70$name`;
`r db[[9]]$variables$V70$varDesc`
```{r}
Crow_V70=modelFitTS_Markdown(db = db[[9]], ts.col = 70, ic.col = 69, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.05, 0.001, 0.1),
                            series=c(0.5, 0.0001, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)) )
```

## Variable `r db[[9]]$variables$V71$name`;
`r db[[9]]$variables$V71$varDesc`
```{r}
Crow_V71=modelFitTS_Markdown(db = db[[9]], ts.col = 71, ic.col = 70, unitConverter = 1e3)
```

## Variable `r db[[9]]$variables$V72$name`;
`r db[[9]]$variables$V72$varDesc`
```{r}
Crow_V72=modelFitTS_Markdown(db = db[[9]], ts.col = 72, ic.col = 71, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.05, 0.001, 0.1),
                            series=c(0.01, 0.0005, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V73$name`;
`r db[[9]]$variables$V73$varDesc`
```{r}
Crow_V73=modelFitTS_Markdown(db = db[[9]], ts.col = 73, ic.col = 72, unitConverter = 1e3)
```

## Variable `r db[[9]]$variables$V74$name`;
`r db[[9]]$variables$V74$varDesc`
```{r}
Crow_V74=modelFitTS_Markdown(db = db[[9]], ts.col = 74, ic.col = 73, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.05, 0.001, 0.1),
                            series=c(0.01, 0.0005, 0.01, 0.1),
                            feedback=c(0.05, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V75$name`;
`r db[[9]]$variables$V75$varDesc`
```{r}
Crow_V75=modelFitTS_Markdown(db = db[[9]], ts.col = 75, ic.col = 74, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.1, 0.005, 0.1),
                            series=c(0.01, 0.005, 0.01, 0.1),
                            feedback=c(0.01, 0.005, 0.01, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V76$name`;
`r db[[9]]$variables$V76$varDesc`
```{r}
##
Crow_V76=modelFitTS_Markdown(db = db[[9]], ts.col = 76, ic.col = 75, unitConverter = 1e3 ,
               inipars=list(oneP=0.5,
                            parallel=c(0.5, 0.001, 0.1),
                            series=c(0.01, 0.0005, 0.01, 0.1),
                            feedback=c(0.05, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V77$name`;
`r db[[9]]$variables$V77$varDesc`
```{r}
Crow_V77=modelFitTS_Markdown(db = db[[9]], ts.col = 77, ic.col = 76, unitConverter = 1e3)
```

## Variable `r db[[9]]$variables$V78$name`;
`r db[[9]]$variables$V78$varDesc`
```{r}
Crow_V78=modelFitTS_Markdown(db = db[[9]], ts.col = 78, ic.col = 77, unitConverter = 1e3,
               inipars=list(oneP=0.5,
                            parallel=c(0.05, 0.001, 0.1),
                            series=c(0.01, 0.0005, 0.01, 0.1),
                            feedback=c(0.01, 0.0005, 0.1, 0.01, 0.1)))
```

## Variable `r db[[9]]$variables$V79$name`;
`r db[[9]]$variables$V79$varDesc`
```{r}
Crow_V79=modelFitTS_Markdown(db = db[[9]], ts.col = 79, ic.col = 78, unitConverter = 1e3)
```

# Dataset `r db[[15]]$citationKey`

```{r, include=FALSE }
#
#
######Dataset "Haddix2011SSSJA" ######
db[[15]]$initConditions[1, "carbonUnits"]
# g/kg
db[[15]]$variables$V2$units
#"mgC/gSoil/d"
#** Note: ** the units of variable reported in the metadata are wrong. The CO2 measeured as microG/gsoil/day.
db[[15]]$timeSeries[, c(2:37)]= db[[15]]$timeSeries[, c(2:37)]*1e-3

```

## Variable `r db[[15]]$variables$V2$name`;
`r db[[15]]$variables$V2$varDesc`
```{r}
Haddix_V2=modelFitTS_Markdown(db = db[[15]], ts.col = 2, ic.col = 1, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.1, 0.001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.1, 0.01, 0.01)) )
```

## Variable `r db[[15]]$variables$V3$name`;
`r db[[15]]$variables$V3$varDesc`
```{r}

Haddix_V3=modelFitTS_Markdown(db = db[[15]], ts.col = 3, ic.col = 1, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.0001, 0.1),
                                  series=c(0.1, 0.0001, 0.01, 0.1),
                                  feedback=c(0.1, 0.0001, 0.1, 0.005, 0.01)))
```

## Variable `r db[[15]]$variables$V4$name`;
`r db[[15]]$variables$V4$varDesc`
```{r}
Haddix_V4=modelFitTS_Markdown(db = db[[15]], ts.col = 4, ic.col = 1, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.1, 0.001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[15]]$variables$V5$name`;
`r db[[15]]$variables$V5$varDesc`
```{r}
Haddix_V5=modelFitTS_Markdown(db = db[[15]], ts.col = 5, ic.col = 2, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.1, 0.001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.05, 0.01, 0.01)))
```

## Variable `r db[[15]]$variables$V6$name`;
`r db[[15]]$variables$V6$varDesc`
```{r}

Haddix_V6=modelFitTS_Markdown(db = db[[15]], ts.col = 6, ic.col = 2, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.01, 0.001, 0.1),
                                  series=c(0.01, 0.001, 0.01, 0.1),
                                  feedback=c(0.01, 0.0001, 0.1, 0.1, 0.01)))
```

## Variable `r db[[15]]$variables$V7$name`;
`r db[[15]]$variables$V7$varDesc`
```{r}
Haddix_V7=modelFitTS_Markdown(db = db[[15]], ts.col = 7, ic.col = 2, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.01, 0.001, 0.1),
                                  series=c(0.01, 0.001, 0.01, 0.1),
                                  feedback=c(0.05, 0.001, 0.01, 0.1, 0.01)))
```

## Variable `r db[[15]]$variables$V8$name`;
`r db[[15]]$variables$V8$varDesc`
```{r}
Haddix_V8=modelFitTS_Markdown(db = db[[15]], ts.col = 8, ic.col = 3, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.1, 0.0001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[15]]$variables$V9$name`;
`r db[[15]]$variables$V9$varDesc`
```{r}
Haddix_V9=modelFitTS_Markdown(db = db[[15]], ts.col = 9, ic.col = 3, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.1, 0.0001, 0.01, 0.1),
                                  feedback=c(0.05, 0.001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[15]]$variables$V10$name`;
`r db[[15]]$variables$V10$varDesc`
```{r}
Haddix_V10=modelFitTS_Markdown(db = db[[15]], ts.col = 10, ic.col = 3, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.01, 0.001, 0.1),
                                  series=c(0.1, 0.0001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[15]]$variables$V11$name`;
`r db[[15]]$variables$V11$varDesc`
```{r}
Haddix_V11=modelFitTS_Markdown(db = db[[15]], ts.col = 11, ic.col = 4, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.1, 0.0001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[15]]$variables$V12$name`;
`r db[[15]]$variables$V12$varDesc`
```{r}
Haddix_V12=modelFitTS_Markdown(db = db[[15]], ts.col = 12, ic.col = 4, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.05, 0.0001, 0.01, 0.1),
                                  feedback=c(0.05, 0.001, 0.01, 0.01, 0.01)))
```

## Variable `r db[[15]]$variables$V13$name`;
`r db[[15]]$variables$V13$varDesc`
```{r}
Haddix_V13=modelFitTS_Markdown(db = db[[15]], ts.col = 13, ic.col = 4, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.001, 0.1),
                                  series=c(0.1, 0.001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.1, 0.01, 0.01)))
```

# Dataset `r db[[19]]$citationKey`
```{r, include=FALSE }
###### Dataset "NeffHooper2002" #######
db[[19]]$variables$V2$units
# "mgC/gSoilC/d"
db[[19]]$initConditions[1,"carbonUnits"]
# percent
```

## Variable `r db[[19]]$variables$V2$name`;
`r db[[19]]$variables$V2$varDesc`
```{r}
Nethooper_V2= modelFitTS_Markdown(db = db[[19]], ts.col = 2, ic.col = 2, unitConverter = 10,
                         inipars=list(oneP=0.5,
                                      parallel=c(0.01, 0.001, 0.01),
                                      series=c(0.01, 0.00001, 0.01, 0.01),
                                      feedback=c(0.01, 0.00001, 0.01, 0.01, 0.05)))
```

## Variable `r db[[19]]$variables$V3$name`;
`r db[[19]]$variables$V3$varDesc`
```{r}
Nethooper_V3= modelFitTS_Markdown(db = db[[19]], ts.col = 3, ic.col = 3, unitConverter = 10,
                         inipars=list(oneP=0.5,
                                      parallel=c(0.01, 0.001, 0.1),
                                      series=c(0.05, 0.0001, 0.01, 0.1),
                                      feedback=c(0.01, 0.0001, 0.01, 0.01, 0.01)))
```

## Variable `r db[[19]]$variables$V4$name`;
`r db[[19]]$variables$V4$varDesc`
```{r}

Nethooper_V4= modelFitTS_Markdown(db = db[[19]], ts.col = 4, ic.col = 4, unitConverter = 10,
                         inipars=list(oneP=0.5,
                                      parallel=c(0.01, 0.001, 0.1),
                                      series=c(0.05, 0.0001, 0.01, 0.1),
                                      feedback=c(0.01, 0.0001, 0.01, 0.01, 0.01)))
```

## Variable `r db[[19]]$variables$V5$name`;
`r db[[19]]$variables$V5$varDesc`
```{r}
Nethooper_V5= modelFitTS_Markdown(db = db[[19]], ts.col = 5, ic.col = 7, unitConverter = 10)
```

## Variable `r db[[19]]$variables$V6$name`;
`r db[[19]]$variables$V6$varDesc`
```{r}
##
Nethooper_V6= modelFitTS_Markdown(db = db[[19]], ts.col = 6, ic.col = 2, unitConverter = 10)
```

## Variable `r db[[19]]$variables$V7$name`;
`r db[[19]]$variables$V7$varDesc`
```{r}
Nethooper_V7= modelFitTS_Markdown(db = db[[19]], ts.col = 7, ic.col = 3, unitConverter = 10)
```

<!-- ```{r} -->
<!-- #so many miising values -->
<!-- #Nethooper_V8= modelFitTS_Markdown(db = db[[19]], ts.col = 8, ic.col = 4, unitConverter = 10) -->
<!-- ``` -->


## Variable `r db[[19]]$variables$V9$name`;
`r db[[19]]$variables$V9$varDesc`
```{r}
Nethooper_V9= modelFitTS_Markdown(db = db[[19]], ts.col = 9, ic.col = 7, unitConverter = 10)
```

## Variable `r db[[19]]$variables$V10$name`;
`r db[[19]]$variables$V10$varDesc`
```{r}

Nethooper_V10= modelFitTS_Markdown(db = db[[19]], ts.col = 10, ic.col = 2, unitConverter = 10,
                          inipars=list(oneP=0.5,
                                       parallel=c(0.01, 0.001, 0.1),
                                       series=c(0.01, 0.0001, 0.01, 0.1),
                                       feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[19]]$variables$V11$name`;
`r db[[19]]$variables$V11$varDesc`
```{r}

Nethooper_V11= modelFitTS_Markdown(db = db[[19]], ts.col = 11, ic.col = 1, unitConverter = 10,
                          inipars=list(oneP=0.5,
                                       parallel=c(0.01, 0.001, 0.1),
                                       series=c(0.05, 0.0001, 0.01, 0.1),
                                       feedback=c(0.05, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[19]]$variables$V12$name`;
`r db[[19]]$variables$V12$varDesc`
```{r}

Nethooper_V12= modelFitTS_Markdown(db = db[[19]], ts.col = 12, ic.col = 4, unitConverter = 10,
                          inipars=list(oneP=0.5,
                                       parallel=c(0.01, 0.001, 0.1),
                                       series=c(0.05, 0.0001, 0.01, 0.1),
                                       feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[19]]$variables$V13$name`;
`r db[[19]]$variables$V13$varDesc`
```{r}

Nethooper_V13= modelFitTS_Markdown(db = db[[19]], ts.col = 13, ic.col = 6, unitConverter = 10,
                          inipars=list(oneP=0.5,
                                       parallel=c(0.01, 0.001, 0.1),
                                       series=c(0.05, 0.0001, 0.01, 0.1),
                                       feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[19]]$variables$V14$name`;
`r db[[19]]$variables$V14$varDesc`
```{r}

Nethooper_V14= modelFitTS_Markdown(db = db[[19]], ts.col = 14, ic.col = 5, unitConverter = 10,
                          inipars=list(oneP=0.5,
                                       parallel=c(0.01, 0.001, 0.1),
                                       series=c(0.01, 0.0001, 0.01, 0.1),
                                       feedback=c(0.01, 0.001, 0.01, 0.1, 0.1)))
```

# Dataset `r db[[22]]$citationKey`
```{r, include=FALSE}
###### Dataset "Rey2008EJSS" ######
db[[22]]$variables$V2$units
# "microgC/gSoil/d"
db[[22]]$initConditions[1, "carbonUnits"]
# percent

## change the units and units label of measured flux from microgC/grSoil/d to mgC/grSoil/d
db[[22]]$timeSeries[, c(2:25)]= db[[22]]$timeSeries[, c(2:25)]*1e-3

for(i in 2:length(db[[22]]$variables[1:25])){
  db[[22]][["variables"]][[i]][["units"]]= "mgC/gSoil/d" }

# Check if the units is correct
# units=list(NULL)
# for(i in 1:length(db[[22]]$variables)){
#   units[[i]]= db[[22]][["variables"]][[i]][["units"]]
# }
# View(units)
```

## Variable `r db[[22]]$variables$V2$name`;
`r db[[22]]$variables$V2$varDesc`
```{r}
Rey_V2= modelFitTS_Markdown(db = db[[22]], ts.col = 2, ic.col = 1, unitConverter = 1,
                   inipars=list(oneP=0.5,
                                parallel=c(0.05, 0.001, 0.01),
                                series=c(0.05, 0.001, 0.01, 0.01),
                                feedback=c(0.05, 0.001, 0.01, 0.01, 0.01)))
```

## Variable `r db[[22]]$variables$V3$name`;
`r db[[22]]$variables$V3$varDesc`
```{r}
Rey_V3= modelFitTS_Markdown(db = db[[22]], ts.col = 3, ic.col = 2, unitConverter = 1,
                   inipars=list(oneP=0.01,
                                parallel=c(0.1, 0.001, 0.01),
                                series=c(0.1, 0.001, 0.01, 0.1),
                                feedback=c(0.01, 0.0001, 0.1, 0.01, 0.01)))
```

## Variable `r db[[22]]$variables$V4$name`;
`r db[[22]]$variables$V4$varDesc`
```{r}
Rey_V4= modelFitTS_Markdown(db = db[[22]], ts.col = 4, ic.col = 3, unitConverter = 1,
                   inipars=list(oneP=0.01,
                                parallel=c(0.01, 0.001, 0.01),
                                series=c(0.01, 0.001, 0.001, 0.01),
                                feedback=c(0.01, 0.001, 0.01, 0.01, 0.01)))
```

## Variable `r db[[22]]$variables$V5$name`;
`r db[[22]]$variables$V5$varDesc`
```{r}
Rey_V5= modelFitTS_Markdown(db = db[[22]], ts.col = 5, ic.col = 4, unitConverter = 1,
                   inipars=list(oneP=0.01,
                                parallel=c(0.01, 0.001, 0.01),
                                series=c(0.01, 0.0001, 0.01, 0.01),
                                feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V6$name`;
`r db[[22]]$variables$V6$varDesc`
```{r}
Rey_V6= modelFitTS_Markdown(db = db[[22]], ts.col = 6, ic.col = 5, unitConverter = 1,
                   inipars=list(oneP=0.01,
                                parallel=c(0.01, 0.001, 0.01),
                                series=c(0.01, 0.0001, 0.01, 0.1),
                                feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V7$name`;
`r db[[22]]$variables$V7$varDesc`
```{r}
Rey_V7= modelFitTS(db = db[[22]], ts.col = 7, ic.col = 6, unitConverter = 1, 
                   inipars=list(oneP=0.01,
                                parallel=c(0.1, 0.001, 0.01), 
                                series=c(0.01, 0.0001, 0.01, 0.1), 
                                feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V8$name`;
`r db[[22]]$variables$V8$varDesc`
```{r}
Rey_V8= modelFitTS_Markdown(db = db[[22]], ts.col = 8, ic.col = 7, unitConverter = 1,
                   inipars=list(oneP=0.01,
                                parallel=c(0.1, 0.001, 0.01),
                                series=c(0.1, 0.001, 0.01, 0.01),
                                feedback=c(0.1, 0.001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V9$name`;
`r db[[22]]$variables$V9$varDesc`
```{r}
Rey_V9= modelFitTS_Markdown(db = db[[22]], ts.col = 9, ic.col = 8, unitConverter = 1,
                   inipars=list(oneP=0.01,
                                parallel=c(0.1, 0.001, 0.1),
                                series=c(0.1, 0.001, 0.1, 0.1),
                                feedback=c(0.1, 0.001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V10$name`;
`r db[[22]]$variables$V10$varDesc`
```{r}
Rey_V10= modelFitTS_Markdown(db = db[[22]], ts.col = 10, ic.col = 9, unitConverter = 1,
                   inipars=list(oneP=0.1,
                                parallel=c(0.1, 0.001, 0.1),
                                series=c(0.01, 0.0001, 0.01, 0.1),
                                feedback=c(0.01, 0.001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V11$name`;
`r db[[22]]$variables$V11$varDesc`
```{r}

Rey_V11= modelFitTS_Markdown(db = db[[22]], ts.col = 11, ic.col = 10, unitConverter = 1,
                    inipars=list(oneP=0.01,
                                 parallel=c(0.1, 0.001, 0.1),
                                 series=c(0.1, 0.001, 0.01, 0.1),
                                 feedback=c(0.1, 0.001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V12$name`;
`r db[[22]]$variables$V12$varDesc`
```{r}
Rey_V12= modelFitTS(db = db[[22]], ts.col = 12, ic.col = 11, unitConverter = 1, 
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1), 
                                 series=c(0.01, 0.0001, 0.01, 0.1), 
                                 feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V13$name`;
`r db[[22]]$variables$V13$varDesc`
```{r}
Rey_V13= modelFitTS(db = db[[22]], ts.col = 13, ic.col = 12, unitConverter = 1, 
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1), 
                                 series=c(0.01, 0.0001, 0.01, 0.1), 
                                 feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V14$name`;
`r db[[22]]$variables$V14$varDesc`
```{r}
Rey_V14= modelFitTS_Markdown(db = db[[22]], ts.col = 14, ic.col = 13, unitConverter = 1,
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.001, 0.01, 0.1),
                                 feedback=c(0.01, 0.001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V15$name`;
`r db[[22]]$variables$V15$varDesc`
```{r}
Rey_V15= modelFitTS(db = db[[22]], ts.col = 15, ic.col = 14, unitConverter = 1, 
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1), 
                                 series=c(0.01, 0.0001, 0.01, 0.1), 
                                 feedback=c(0.01, 0.0001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V16$name`;
`r db[[22]]$variables$V16$varDesc`
```{r}
Rey_V16= modelFitTS_Markdown(db = db[[22]], ts.col = 16, ic.col = 15, unitConverter = 1,
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.001, 0.01, 0.1),
                                 feedback=c(0.01, 0.001, 0.1, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V17$name`;
`r db[[22]]$variables$V17$varDesc`
```{r}
Rey_V17= modelFitTS(db = db[[22]], ts.col = 17, ic.col = 16, unitConverter = 1, 
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1), 
                                 series=c(0.01, 0.0001, 0.01, 0.1), 
                                 feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V18$name`;
`r db[[22]]$variables$V18$varDesc`
```{r}
Rey_V18= modelFitTS_Markdown(db = db[[22]], ts.col = 18, ic.col = 17, unitConverter = 1,
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.001, 0.01, 0.1),
                                 feedback=c(0.01, 0.001, 0.001, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V19$name`;
`r db[[22]]$variables$V19$varDesc`
```{r}
Rey_V19= modelFitTS_Markdown(db = db[[22]], ts.col = 19, ic.col = 18, unitConverter = 1,
                    inipars=list(oneP=0.01,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.001, 0.01, 0.1),
                                 feedback=c(0.01, 0.001, 0.001, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V20$name`;
`r db[[22]]$variables$V20$varDesc`
```{r}
Rey_V20= modelFitTS_Markdown(db = db[[22]], ts.col = 20, ic.col = 19, unitConverter = 1,
                    inipars=list(oneP=0.1,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.0001, 0.01, 0.1),
                                 feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V21$name`;
`r db[[22]]$variables$V21$varDesc`
```{r}
Rey_V21= modelFitTS_Markdown(db = db[[22]], ts.col = 21, ic.col = 20, unitConverter = 1,
                    inipars=list(oneP=0.1,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.0001, 0.01, 0.1),
                                 feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V22$name`;
`r db[[22]]$variables$V22$varDesc`
```{r}
Rey_V22= modelFitTS_Markdown(db = db[[22]], ts.col = 22, ic.col = 21, unitConverter = 1,
                    inipars=list(oneP=0.1,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.0001, 0.01, 0.1),
                                 feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V23$name`;
`r db[[22]]$variables$V23$varDesc`
```{r}
Rey_V23= modelFitTS_Markdown(db = db[[22]], ts.col = 23, ic.col = 22, unitConverter = 1,
                    inipars=list(oneP=0.1,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.0001, 0.001, 0.1),
                                 feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V24$name`;
`r db[[22]]$variables$V24$varDesc`
```{r}
Rey_V24= modelFitTS_Markdown(db = db[[22]], ts.col = 24, ic.col = 23, unitConverter = 1,
                    inipars=list(oneP=0.1,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.0001, 0.01, 0.1),
                                 feedback=c(0.01, 0.001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[22]]$variables$V25$name`;
`r db[[22]]$variables$V25$varDesc`
```{r}
Rey_V25= modelFitTS_Markdown(db = db[[22]], ts.col = 25, ic.col = 24, unitConverter = 1,
                    inipars=list(oneP=0.1,
                                 parallel=c(0.01, 0.001, 0.1),
                                 series=c(0.01, 0.001, 0.001, 0.5),
                                 feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

# Dataset `r db[[24]]$citationKey `
```{r, include=FALSE}
############ Start with Sierra2017BG ############
#All models needs to be revised
# The respiration unit is microgr C/day
# th unit of iniC is still unclear
db[[24]]$timeSeries[, c(2:17)]= db[[24]]$timeSeries[, c(2:17)]*1e-3
```

## Variable `r db[[24]]$variables$V2$name`;
`r db[[24]]$variables$V2$varDesc`
```{r}
Sierra_V2=modelFitTS_Markdown(db = db[[24]], ts.col = 2, ic.col = 1, unitConverter = 0.01,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.5, 0.01, 0.5),
                                  series=c(0.5, 0.01, 0.01, 0.5),
                                  feedback=c(0.1, 0.01, 0.01, 0.1, 0.5)))
```

## Variable `r db[[24]]$variables$V3$name`;
`r db[[24]]$variables$V3$varDesc`
```{r}
##
Sierra_V3=modelFitTS_Markdown(db = db[[24]], ts.col = 3, ic.col = 1, unitConverter = 0.01,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.5, 0.01, 0.5),
                                  series=c(0.5, 0.01, 0.01, 0.5),
                                  feedback=c(0.1, 0.01, 0.01, 0.1, 0.5)))
```

## Variable `r db[[24]]$variables$V4$name`;
`r db[[24]]$variables$V4$varDesc`
```{r}
Sierra_V4=modelFitTS_Markdown(db = db[[24]], ts.col = 4, ic.col = 1, unitConverter = 0.01,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.5, 0.01, 0.5),
                                  series=c(0.5, 0.01, 0.01, 0.5),
                                  feedback=c(0.5, 0.01, 0.1, 0.01, 0.1)))
```

## Variable `r db[[24]]$variables$V5$name`;
`r db[[24]]$variables$V5$varDesc`
```{r}
Sierra_V5=modelFitTS_Markdown(db = db[[24]], ts.col = 5, ic.col = 1, unitConverter = 0.01,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.1, 0.05, 0.5),
                                  series=c(0.1, 0.01, 0.01, 0.5),
                                  feedback=c(0.1, 0.01, 0.5, 0.01, 0.5)))
```

## Variable `r db[[24]]$variables$V6$name`;
`r db[[24]]$variables$V6$varDesc`
```{r}
Sierra_V6=modelFitTS_Markdown(db = db[[24]], ts.col = 6, ic.col = 1, unitConverter = 0.1,
                     inipars=list(oneP=0.01,
                                  parallel=c(0.5, 0.01, 0.5),
                                  series=c(0.5, 0.01, 0.01, 0.5),
                                  feedback=c(0.5, 0.01, 0.1, 0.01, 0.1)))
```

## Variable `r db[[24]]$variables$V7$name`;
`r db[[24]]$variables$V7$varDesc`
```{r}

Sierra_V7=modelFitTS_Markdown(db = db[[24]], ts.col = 7, ic.col = 1, unitConverter = 0.1,
                     inipars=list(oneP=0.1,
                                  parallel=c(0.1, 0.01, 0.1),
                                  series=c(0.1, 0.001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.01, 0.1, 0.1)))
```

## Variable `r db[[24]]$variables$V8$name`;
`r db[[24]]$variables$V8$varDesc`
```{r}

Sierra_V8=modelFitTS_Markdown(db = db[[24]], ts.col = 8, ic.col = 1, unitConverter = 0.1,
                     inipars=list(oneP=0.1,
                                  parallel=c(0.1, 0.001, 0.01),
                                  series=c(0.1, 0.001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.01, 0.1, 0.1)))
```

## Variable `r db[[24]]$variables$V9$name`;
`r db[[24]]$variables$V9$varDesc`
```{r}
Sierra_V9=modelFitTS_Markdown(db = db[[24]], ts.col = 9, ic.col = 1, unitConverter = 0.1,
                     inipars=list(oneP=0.1,
                                  parallel=c(0.1, 0.001, 0.01),
                                  series=c(0.1, 0.001, 0.01, 0.1),
                                  feedback=c(0.1, 0.001, 0.01, 0.1, 0.1)))
```

## Variable `r db[[24]]$variables$V10$name`;
`r db[[24]]$variables$V10$varDesc`
```{r}

Sierra_V10=modelFitTS_Markdown(db = db[[24]], ts.col = 10, ic.col = 1, unitConverter = 0.01,
                      inipars=list(oneP=0.1,
                                   parallel=c(0.1, 0.01, 0.1),
                                   series=c(0.05, 0.005, 0.01, 0.1),
                                   feedback=c(0.05, 0.005, 0.01, 0.01, 0.1)))
```

## Variable `r db[[24]]$variables$V11$name`;
`r db[[24]]$variables$V11$varDesc`
```{r}

Sierra_V11=modelFitTS_Markdown(db = db[[24]], ts.col = 11, ic.col = 1, unitConverter = 0.01,
                      inipars=list(oneP=0.1,
                                   parallel=c(0.1, 0.001, 0.01),
                                   series=c(0.05, 0.0005, 0.01, 0.1),
                                   feedback=c(0.05, 0.0005, 0.01, 0.01, 0.1)))
```

## Variable `r db[[24]]$variables$V12$name`;
`r db[[24]]$variables$V12$varDesc`
```{r}

Sierra_V12=modelFitTS_Markdown(db = db[[24]], ts.col = 12, ic.col = 1, unitConverter = 0.01,
                      inipars=list(oneP=0.01,
                                   parallel=c(0.5, 0.005, 0.5),
                                   series=c(0.05, 0.005, 0.05, 0.5),
                                   feedback=c(0.05, 0.005, 0.005, 0.05, 0.5)))

```

## Variable `r db[[24]]$variables$V13$name`;
`r db[[24]]$variables$V13$varDesc`
```{r}
Sierra_V13=modelFitTS_Markdown(db = db[[24]], ts.col = 13, ic.col = 1, unitConverter = 0.01,
                      inipars=list(oneP=0.01,
                                   parallel=c(0.5, 0.005, 0.5),
                                   series=c(0.05, 0.005, 0.05, 0.5),
                                   feedback=c(0.05, 0.005, 0.005, 0.05, 0.5)))

```

## Variable `r db[[24]]$variables$V14$name`;
`r db[[24]]$variables$V14$varDesc`
```{r}
Sierra_V14=modelFitTS_Markdown(db = db[[24]], ts.col = 14, ic.col = 1, unitConverter = 0.01,
                      inipars=list(oneP=0.01,
                                   parallel=c(0.5, 0.005, 0.5),
                                   series=c(0.05, 0.005, 0.05, 0.5),
                                   feedback=c(0.05, 0.005, 0.005, 0.05, 0.5)))

```

## Variable `r db[[24]]$variables$V15$name`;
`r db[[24]]$variables$V15$varDesc`
```{r}
Sierra_V15=modelFitTS(db = db[[24]], ts.col = 15, ic.col = 1, unitConverter = 0.01, 
                      inipars=list(oneP=0.01,
                                   parallel=c(0.5, 0.005, 0.5),
                                   series=c(0.05, 0.005, 0.05, 0.5),
                                   feedback=c(0.05, 0.005, 0.05, 0.05, 0.5)))

```

## Variable `r db[[24]]$variables$V16$name`;
`r db[[24]]$variables$V16$varDesc`
```{r}
Sierra_V16=modelFitTS_Markdown(db = db[[24]], ts.col = 16, ic.col = 1, unitConverter = 0.01,
                      inipars=list(oneP=0.01,
                                   parallel=c(0.5, 0.005, 0.5),
                                   series=c(0.05, 0.005, 0.05, 0.5),
                                   feedback=c(0.05, 0.005, 0.005, 0.05, 0.5)))

```

## Variable `r db[[24]]$variables$V17$name`;
`r db[[24]]$variables$V17$varDesc`
```{r}
Sierra_V17=modelFitTS_Markdown(db = db[[24]], ts.col = 17, ic.col = 1, unitConverter = 0.01,
                      inipars=list(oneP=0.01,
                                   parallel=c(0.5, 0.005, 0.5),
                                   series=c(0.05, 0.005, 0.05, 0.5),
                                   feedback=c(0.05, 0.005, 0.005, 0.05, 0.5)))
```

# Dataset `r db[[30]]$citationKey`

```{r, include=FALSE}

######### Dataset "Winkler1996" ######
db[[30]]$variables$V2$units
# "micromolC-CO2/g/d"
db[[30]]$initConditions[1, "carbonUnits"]
# percent
# Change the unit from micromol to milimol
db[[30]]$timeSeries[, c(2:12)]= db[[30]]$timeSeries[, c(2:12)]*1e-3

for(i in 2:length(db[[30]]$variables[1:12])){
  db[[30]][["variables"]][[i]][["units"]]= "mmolC/gSoil/d" }


#So many miising values datasets
#Winkler_V2=modelFitTS_Markdown(db = db[[30]], ts.col = 2, ic.col = 1, unitConverter = 1)
#Winkler_V3=modelFitTS_Markdown(db = db[[30]], ts.col = 3, ic.col = 3, unitConverter = 1)
#Winkler_V4=modelFitTS_Markdown(db = db[[30]], ts.col = 4, ic.col = 2, unitConverter = 1)

```

## Variable `r db[[30]]$variables$V5$name`;
`r db[[30]]$variables$V5$varDesc`
```{r}
Winkler_V5=modelFitTS_Markdown(db = db[[30]], ts.col = 5, ic.col = 1, unitConverter = 1,
                      inipars=list(oneP=0.1,
                                   parallel=c(0.01, 0.001, 0.1),
                                   series=c(0.01, 0.0001, 0.01, 0.5),
                                   feedback=c(0.01, 0.0001, 0.01, 0.01, 0.5)))

```

## Variable `r db[[30]]$variables$V6$name`;
`r db[[30]]$variables$V6$varDesc`
```{r}
Winkler_V6=modelFitTS_Markdown(db = db[[30]], ts.col = 6, ic.col = 3, unitConverter = 1,
                      inipars=list(oneP=0.01,
                                   parallel=c(0.5, 0.05, 0.5),
                                   series=c(0.05, 0.0005, 0.01, 0.5),
                                   feedback=c(0.01, 0.001, 0.1, 0.01, 0.5)))

```

## Variable `r db[[30]]$variables$V7$name`;
`r db[[30]]$variables$V7$varDesc`
```{r}
Winkler_V7=modelFitTS_Markdown(db = db[[30]], ts.col = 7, ic.col = 2, unitConverter = 1,
                      inipars=list(oneP=0.01,
                                   parallel=c(0.01, 0.001, 0.1),
                                   series=c(0.01, 0.0001, 0.01, 0.1),
                                   feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))

```

## Variable `r db[[30]]$variables$V8$name`;
`r db[[30]]$variables$V8$varDesc`
```{r}
Winkler_V8=modelFitTS_Markdown(db = db[[30]], ts.col = 8, ic.col = 1, unitConverter = 0.1,
                      inipars=list(oneP=0.05,
                                   parallel=c(0.01, 0.001, 0.1),
                                   series=c(0.01, 0.0001, 0.01, 0.1),
                                   feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[30]]$variables$V9$name`;
`r db[[30]]$variables$V9$varDesc`
```{r}
Winkler_V9=modelFitTS_Markdown(db = db[[30]], ts.col = 9, ic.col = 3, unitConverter = 1,
                      inipars=list(oneP=0.05,
                                   parallel=c(0.01, 0.001, 0.1),
                                   series=c(0.01, 0.0001, 0.01, 0.1),
                                   feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

## Variable `r db[[30]]$variables$V10$name`;
`r db[[30]]$variables$V10$varDesc`
```{r}
Winkler_V10=modelFitTS_Markdown(db = db[[30]], ts.col = 10, ic.col = 2, unitConverter = 1,
                       inipars=list(oneP=0.05,
                                    parallel=c(0.01, 0.001, 0.1),
                                    series=c(0.01, 0.0005, 0.01, 0.1),
                                    feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))
```

<!-- ```{r} -->


<!-- # Winkler_V11=modelFitTS_Markdown(db = db[[30]], ts.col = 11, ic.col = 1, unitConverter = 1, -->
<!-- #                        inipars=list(oneP=0.05, -->
<!-- #                                     parallel=c(0.01, 0.001, 0.1), -->
<!-- #                                     series=c(0.01, 0.0001, 0.01, 0.1), -->
<!-- #                                     feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1))) -->
<!-- ``` -->


## Variable `r db[[30]]$variables$V12$name`;
`r db[[30]]$variables$V12$varDesc`
```{r}
Winkler_V12=modelFitTS_Markdown(db = db[[30]], ts.col = 12, ic.col = 3, unitConverter = 1,
                       inipars=list(oneP=0.05,
                                    parallel=c(0.01, 0.001, 0.1),
                                    series=c(0.01, 0.0001, 0.01, 0.1),
                                    feedback=c(0.01, 0.0001, 0.01, 0.01, 0.1)))

```

# Dataset `r db[[31]]$citationKey`
```{r, include=FALSE}
####### Dataset "Zhang2007" ########
db[[31]]$variables$V2$units
# "mgC/gC/day"
db[[31]]$initConditions[1, "carbonUnits"]
# percent
```

## Variable `r db[[31]]$variables$V2$name`;
`r db[[31]]$variables$V2$varDesc`
```{r}
Zhang_V2=modelFitTS_Markdown(db = db[[31]], ts.col = 2, ic.col = 1, unitConverter = 10,
                    inipars=list(oneP=0.5,
                                 parallel=c(0.1, 0.01, 0.1),
                                 series=c(0.1, 0.01, 0.01, 0.1),
                                 feedback=c(0.1, 0.01, 0.01, 0.1, 0.1)))


```

## Variable `r db[[31]]$variables$V3$name`;
`r db[[31]]$variables$V3$varDesc`
```{r}
Zhang_V3=modelFitTS_Markdown(db = db[[31]], ts.col = 3, ic.col = 2, unitConverter = 10,
                    inipars=list(oneP=0.5,
                                 parallel=c(0.1, 0.01, 0.1),
                                 series=c(0.1, 0.001, 0.01, 0.1),
                                 feedback=c(0.1, 0.01, 0.01, 0.01, 0.1)))

```

## Variable `r db[[31]]$variables$V4$name`;
`r db[[31]]$variables$V4$varDesc`
```{r}
Zhang_V4=modelFitTS_Markdown(db = db[[31]], ts.col = 4, ic.col = 3, unitConverter = 10,
                    inipars=list(oneP=0.5,
                                 parallel=c(0.1, 0.01, 0.1),
                                 series=c(0.1, 0.001, 0.01, 0.1),
                                 feedback=c(0.1, 0.001, 0.01, 0.01, 0.1)))

```

## Variable `r db[[31]]$variables$V5$name`;
`r db[[31]]$variables$V5$varDesc`
```{r}
Zhang_V5=modelFitTS_Markdown(db = db[[31]], ts.col = 5, ic.col = 1, unitConverter = 10,
                    inipars=list(oneP=0.5,
                                 parallel=c(0.1, 0.01, 0.1),
                                 series=c(0.1, 0.01, 0.01, 0.1),
                                 feedback=c(0.1, 0.01, 0.01, 0.1, 0.1)))

```

## Variable `r db[[31]]$variables$V6$name`;
`r db[[31]]$variables$V6$varDesc`
```{r}
Zhang_V6=modelFitTS_Markdown(db = db[[31]], ts.col = 6, ic.col = 2, unitConverter = 10,
                    inipars=list(oneP=0.01,
                                 parallel=c(0.1, 0.01, 0.1),
                                 series=c(0.1, 0.01, 0.01, 0.1),
                                 feedback=c(0.1, 0.01, 0.01, 0.1, 0.1)))

```

## Variable `r db[[31]]$variables$V7$name`;
`r db[[31]]$variables$V7$varDesc`
```{r}
Zhang_V7=modelFitTS_Markdown(db = db[[31]], ts.col = 7, ic.col = 3, unitConverter = 10,
                    inipars=list(oneP=0.01,
                                 parallel=c(0.1, 0.05, 0.1),
                                 series=c(0.1, 0.01, 0.01, 0.1),
                                 feedback=c(0.1, 0.01, 0.01, 0.1, 0.1)))




```

# End
