---
title: "Testing multi models to data (Cummulative)"
author: "Mina Azizi-Rad"
date: " "
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(sidb)
library(SoilR)
rm(list=ls())
```

## Testing multi models to the datasets of SidB database




```{r sidb database, results='hide'}
db=loadEntries(path="~/sidb/data/")
db_flat=flatterSIDb(db)
```

```{r inipairs}
twopp_inipars= c(0.01, 0.001, 0.1)
twops_inipars= c(0.005, 0.00001, 0.1, 0.01)
twopf_inipars= c(0.005, 0.00001, 0.1, 0.01, 0.01)
```


# Dataset `r db[[2]]$citationKey`
In this dataset the CO2 respiraton has been reported as cumulative. 
mean initial carbon  


```{r,  results='hide'}
ds2=db[[2]]
plotEntry(db[[2]])
```

```{r}
# Fit the two parallel pool model
#Mod1_2=twoppFit(timeSeries = ds2$timeSeries[, c(1,2)],
#                initialCarbon =ds2$initConditions[2,"carbonMean"]*10000, 
#                inipars =c(0.01, 0.001, 0.1))
#                
# Fit two feedback poolmodel                
#Mod2_2=twopfFit(timeSeries = ds2$timeSeries[, c(1,2)], initialCarbon = ds2$initConditions[2, "carbonMean"]*10000, 
#                inipars = c(0.005, 1e-5, 0.1, 0.01, 0.01))
#Mod3_2=twopsFit(timeSeries = ds2$timeSeries[ , c(1,2)], initialCarbon = ds2$initConditions[2, "carbonMean"]*1e4, 
#                inipars = c(0.005, 1e-5, 0.1, 0.01))
```
 

\newpage

# Dataset `r db[[5]]$citationKey` 

This data set is cummulative
```{r, results='hide'}
ds5 <- db[[5]]
str(ds5$timeSeries)
isCumulative(data.frame(ds5$timeSeries$time,  ds5$timeSeries$C_30deg_CL) )
plotEntry(db[[5]])
```



\newpage

# Dataset `r db[[7]]$citationKey` 

A dataset with 41 variables of `r db_flat$vars$Conant2008[1, "incDesc"] ` in three levels of temperature (4, 15, 25)
The dataset is cumulative

```{r, results='hide'}
ds7 <- db[[7]]
str(ds7$timeSeries)
isCumulative(data.frame(ds7$timeSeries$time,  ds7$timeSeries$ND.CU.4) )
```


\newpage

# Dataset `r db[[8]]$citationKey` 

A dataset with 29 variables of `r db_flat$vars$Craine2010NatGeo[1, "incDesc"] ` 

It is not clear if the dataset is cummulative or not

```{r, results='hide'}
ds8 <- db[[8]]
str(ds8$timeSeries)
isCumulative(data.frame(ds8$timeSeries$time,  ds8$timeSeries$Cumresp_WR) )
plotEntry(db[[8]])
```

```{r}
iniC_CDR=ds8$initConditions[1, "meanCorbon"]
iniC_KBS=ds8$initConditions[2, "meanCarbon"]
```

## V2: Dataset `r db[[8]]$citationKey`, variable `r ds8$variables$V2$name`, site `r ds8$variables$V2$temperature`
```{r}
Mod1_82=twoppFit(timeSeries = ds8$timeSeries[, c(1,2)], initialCarbon =ds8$initConditions[1, "carbonMean"]*1e5 , inipars = twopp_inipars)
Mod2_82=twopfFit(timeSeries = ds8$timeSeries[, c(1,2)], initialCarbon =ds8$initConditions[1, "carbonMean"]*1e5 , inipars = twopf_inipars)
Mod3_82=twopsFit(timeSeries = ds8$timeSeries[, c(1,2)], initialCarbon =ds8$initConditions[1, "carbonMean"]*1e5 , inipars = twops_inipars)
```


## V3: Dataset `r db[[8]]$citationKey`, variable `r ds8$variables$V3$name`, site `r ds8$variables$V3$temperature`
```{r}
Mod1_83=twoppFit(timeSeries = ds8$timeSeries[, c(1,3)], initialCarbon =ds8$initConditions[2, "carbonMean"]*1e5 , inipars = twopp_inipars)
#Mod2_83=twopfFit(timeSeries = ds8$timeSeries[, c(1,3)], initialCarbon =ds8$initConditions[2, "carbonMean"]*1e5 , inipars = twopf_inipars)
Mod3_83=twopsFit(timeSeries = ds8$timeSeries[, c(1,3)], initialCarbon =ds8$initConditions[2, "carbonMean"]*1e5 , inipars = twops_inipars)
```



## V5: Dataset `r db[[8]]$citationKey`, variable `r ds8$variables$V5$name`, site `r ds8$variables$V5$temperature`
```{r}
Mod1_85=twoppFit(timeSeries = ds8$timeSeries[, c(1,5)], initialCarbon =ds8$initConditions[4, "carbonMean"]*1e5 , inipars = twopp_inipars)
Mod2_85=twopfFit(timeSeries = ds8$timeSeries[, c(1,5)], initialCarbon =ds8$initConditions[4, "carbonMean"]*1e5 , inipars = twopf_inipars)
Mod3_85=twopsFit(timeSeries = ds8$timeSeries[, c(1,5)], initialCarbon =ds8$initConditions[4, "carbonMean"]*1e5 , inipars = twops_inipars)
```

## V6: Dataset `r db[[8]]$citationKey`, variable `r ds8$variables$V6$name`, site `r ds8$variables$V6$temperature`
```{r}
Mod1_86=twoppFit(timeSeries = ds8$timeSeries[, c(1,6)], initialCarbon =ds8$initConditions[5, "carbonMean"]*1e5 , inipars = twopp_inipars)
Mod2_86=twopfFit(timeSeries = ds8$timeSeries[, c(1,6)], initialCarbon =ds8$initConditions[5, "carbonMean"]*1e5 , inipars = twopf_inipars)
Mod3_86=twopsFit(timeSeries = ds8$timeSeries[, c(1,6)], initialCarbon =ds8$initConditions[5, "carbonMean"]*1e5 , inipars = twops_inipars)
```


\newpage

# Dataset `r db[[10]]$citationKey` 

A dataset with 28 variables of `r db_flat$vars$Crow2019b[1, "incDesc"] ` , with 3 levels of temperature (16, 21, 26)
in 9 different sites

This dataset is cumulative. 
```{r, results='hide'}
ds10 <- db[[10]]
str(ds10$timeSeries)
isCumulative(data.frame(ds10$timeSeries$time,  ds10$timeSeries$SPE800_16C) )
```


## V2: Dataset `r db[[10]]$citationKey`, variable `r ds10$variables$V2$name`, site `r ds10$variables$V2$site`, temperature `r ds10$variabels$V2$temperature`

```{r}
#Mod1_102=twoppFit(timeSeries = ds10$timeSeries[, c(1,2)], initialCarbon =ds10$initConditions[1, "carbonMean"]*1e5 , inipars = twopp_inipars)
#Mod2_102=twopfFit(timeSeries = ds10$timeSeries[, c(1,2)], initialCarbon =ds10$initConditions[1, "carbonMean"]*1e5 , inipars = twopf_inipars)
#Mod3_102=twopsFit(timeSeries = ds10$timeSeries[, c(1,2)], initialCarbon =ds10$initConditions[1, "carbonMean"]*1e5 , inipars = twops_inipars)
```



\newpage

# Dataset `r db[[13]]$citationKey` 

A dataset with 2 variables of `r db_flat$vars$Fontaine2007[1, "incDesc"] ` , one variable of cellulose amended and one control

This dataset is cumulative.
```{r, results='hide'}
ds13 <- db[[13]]
str(ds13$timeSeries)
isCumulative(data.frame(ds13$timeSeries$time,  ds13$timeSeries$cellulose) )
plotEntry(ds13)
```



\newpage

# Dataset `r db[[14]]$citationKey` 

A dataset with 5 variables of `r db_flat$vars$Gillabel2010GCB[1, "incDesc"] ` 

This dataset is cumulative
```{r, results='hide'}
ds14 <- db[[14]]
str(ds14$timeSeries)
isCumulative(data.frame(ds14$timeSeries$time,  ds14$timeSeries$C_Top_25) )
plotEntry(db[[14]])
```

\newpage
# Dataset `r db[[16]]$citationKey` 

A dataset with 15 variables of `r db_flat$vars$Hopkins2006[1, "incDesc"] ` 6 different soil types

This dataset is cumulative. 
```{r, results='hide'}
db[[16]]$citationKey
ds16 <- db[[16]]
str(ds16$timeSeries)
isCumulative(data.frame(ds16$timeSeries$time,  ds16$timeSeries$CO2C_DeMin_DeS) )
plotEntry(ds16)
```


\newpage
# Dataset `r db[[18]]$citationKey` 

A dataset with 15 variables of `r db_flat$vars$Lavoie2011JGR[1, "incDesc"] ` 2 different sites, 2 levels of temperature as treatment (5,15) 

This dataset is cumulative
```{r, results='hide'}
db[[18]]$citationKey
ds18 <- db[[18]]
str(ds18$timeSeries)
isCumulative(data.frame(ds18$timeSeries$time,  ds18$timeSeries$TAO_5) )
plotEntry(db[[18]])
```



\newpage
# Dataset `r db[[20]]$citationKey` 

A dataset with 36 variables of `r db_flat$vars$Niklinska1999[1, "incDesc"] `.

** This dataset is too short. There is only 7 observation per variables **
** This dataset is cumulative **
```{r, results='hide'}
db[[20]]$citationKey
ds20 <- db[[20]]
str(ds20$timeSeries)
isCumulative(data.frame(ds20$timeSeries$time,  ds20$timeSeries$CO2_HarNS_5) )
plotEntry(db[[20]])
```


\newpage
# Dataset `r db[[21]]$citationKey` 

A dataset with 13 variables of `r db_flat$vars$Reichstein2000[1, "incDesc"] ` 
** This dataset is cumulative **
```{r, results='hide'}
db[[21]]$citationKey
ds21 <- db[[21]]
str(ds21$timeSeries)
isCumulative(data.frame(ds21$timeSeries$time,  ds21$timeSeries$CMin_Ridge_5) )
plotEntry(ds21)
```


\newpage
# Dataset `r db[[23]]$citationKey` 

A dataset with 7 variables of `r db_flat$vars$Salome2010GCB[1,"incDesc"] ` 

** the dataset is cumulative **
** The dataset is too short. 6 observation **
```{r, results='hide'}
db[[23]]$citationKey
ds23 <- db[[23]]
str(ds23$timeSeries)
isCumulative(data.frame(ds23$timeSeries$time,  ds23$timeSeries$surf_undisturbed) )
plotEntry(ds23)
```



\newpage
# Dataset `r db[[26]]$citationKey` 

A dataset with 15 variables of `r db_flat$vars$Stewart2008SBB[1,"incDesc"] `.

** The dataset is cumulative **
```{r, results='hide'}
db[[26]]$citationKey
ds26 <- db[[26]]
str(ds26$timeSeries)
isCumulative(data.frame(ds26$timeSeries$time,  ds26$timeSeries$Cumresp_A_IA) )
plotEntry(ds26)
```


\newpage
# Dataset `r db[[29]]$citationKey` 

A dataset with 31 variables of `r db_flat$vars$WicklandNeff2008[1,"incDesc"] `. 10 observation

** this dataset is cumulative **
```{r, results='hide'}
db[[29]]$citationKey
ds29 <- db[[29]]
str(ds29$timeSeries)
isCumulative(data.frame(ds29$timeSeries$time,  ds29$timeSeries$C_WD_10_2) )
plotEntry(ds29)
```


