---
title: "sidbQueryReportPlot"
author: "J. Beem-Miller"
date: "28 June 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sidbQueryReportPlot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
**_Delete/comment the "eval = FALSE" line of this first code chunk or the script won't run!_**
```{r setup}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
  )
```


# A simple workflow for querying, generating reports, and plotting data with SIDb
In this vignette we will: 1) build SIDb and flatten the data structure, 2&3) show how to filter and subset the timeseries observations based on user criteria (e.g. exclude standard deviation/standard error timeseries, and only show incubations conducted between 10 and 20 degrees C), and 4) make a few example plots. 

## Install latest version of SIDb and load relevant libraries
```{r libraries}
devtools::install_github("SoilBGC-Datashare/sidb/Rpkg")
library(sidb)
library(ggplot2)
library(plyr)
library(dplyr)
```

## 1. Prepare data
```{r prep}
# load data
database <- loadEntries("~/sidb/data/")

# run "flatter" fx 
db <- flatterSIDB(database)

# join variables dataframes with initConditions
vars.ic <- lapply(seq_along(database), function(i) left_join(db$vars[[i]], database[[i]][["initConditions"]]))
names(vars.ic) <- names(database)

# remove NA columns from vars.ic
vars.ic <- lapply(vars.ic, function(x) x[ ,!apply(is.na(x),2,all)])

# create df object of timeseries list
ts.df <- do.call("rbind", db$timeseries)
```

## 2. Filter *vars.dfl* to exclude SD and SE timeseries
```{r filter}
# add statistic column to entries missing it
vars.dfl.mean <- lapply(vars.ic, function(x) {
  if(is.null(x$statistic)) {
    x$statistic = NA
  } else {
    x$statistic = x$statistic
  }
  return(x)
})
vars.dfl.mean <- lapply(vars.dfl.mean, function(x) {
  x = x[which(x$statistic == "none" | is.na(x$statistic)),]
  return(x)
})
```

## 3. Extract all timeseries with temperature between 10 and 20 degrees
```{r subset, warning=FALSE}
# list variables in vars.dfl by calling 'names' on each element of list and filtering to unique values
sort(unique(unlist(lapply(vars.dfl.mean, function(x) names(x)))))

# first extract indices of studies with timeseries that match conditions
ix.ls <- lapply(vars.dfl.mean, function(x) which(x$temperature >= 10 & x$temperature <= 20))

# then subset list with list of indices and convert to dataframe
t.10.20.df <- plyr::rbind.fill(lapply(seq_along(vars.dfl.mean), function(i) vars.dfl.mean[[i]][ix.ls[[i]],]))

# join your subset of the variables dataframes with the corresponding timeseries
t.10.20.df <- dplyr::left_join(t.10.20.df, ts.df, by="ID")
```

## 4. Make some plots
### a) plot first 300 days, with latitude as color
```{r plot1}
ggplot(t.10.20.df, aes(time, response, color=abs(latitude))) +
  geom_path() +
  scale_x_continuous(limits=c(0,300)) +
  theme_bw() +
  theme(panel.grid = element_blank())
```

### b) plot sites >60N, with moisture as color, first 100 days of incubation
```{r plot2}
# first filter based on moisture units, then plot
filter(t.10.20.df, latitude >= 60) %>% filter(moisture.units == "percentFieldCapacity") %>%
  ggplot(., aes(time, response, color=moisture)) +
  geom_path() +
  scale_x_continuous(limits=c(0,100)) +
  theme_bw() +
  theme(panel.grid = element_blank())
```

### c) plot first 30 days, with moisture as color
```{r plot3}
ggplot(t.10.20.df, aes(time, response, color=moisture)) +
  geom_path() +
  scale_x_continuous(limits=c(0,30)) +
  scale_y_continuous(limits=c(0,1.3e+05)) +
  scale_color_continuous(limits=c(0,100)) +
  theme_bw() +
  theme(panel.grid = element_blank())
```
